---
title: "FY21 In-State vs Out-State Traffic to the University's Main and Admissions' Landing Pages"
author: "Office of Marketing and Brand Management at the University of Southern Maine"
date: "9/10/2020"
output: pdf_document
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}
  - \posttitle{\end{center}}
    \includegraphics[width=2in,height=2in]{C:/Users/christine.iyer/Pictures/Logo.PNG}\LARGE\\}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(dplyr)
library(tidyr)
library(knitr)
```

## Basic Description:

Ask requested by the Director of the Office of Marketing and Brand Management, the information provided in this report pertains to a year over year (FY19 and FY20) change in the amount of web traffic to the University's main landing page, \href{https://usm.maine.edu/}{{\color{blue}{\underline{usm.maine.edu}}}}, and the Office of Admissions' main landing page, \href{https://usm.maine.edu/office-of-admissions}{{\color{blue}{\underline{usm.maine.edu/office-of-admissions}}}} and compares in-state and out-of-state unique page views.

## Findings

### Main Landing Page


```{r}
GA_thisWk <- read.csv("C:/Users/christine.iyer/Box/FY21 Special Projects/FY21 In-StatevsOut-State-Web-Main/main-page.csv", header = T, stringsAsFactors = F)

kable(GA_thisWk %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         Location = ifelse(region == "Maine", "In-State", "Out-of-State"), 
         FY = ifelse(date < "2019-07-01", "FY19", 
                     ifelse(date > "2020-06-30", "FY21", "FY20"))) %>% 
  group_by(FY, Location) %>% summarise(UPV = sum(uniquePageviews)) %>% 
  spread(FY, UPV) %>% 
  select(-FY21) %>% 
  mutate(PctDif= paste0(round((FY20-FY19)/FY19 * 100,2),"%"),
         FY19 = prettyNum(FY19, big.mark = ","), 
         FY20 = prettyNum(FY20, big.mark = ",")) )
```


### Admissions Main Page


```{r}
GA_thisWk_Admit <- read.csv("C:/Users/christine.iyer/Box/FY21 Special Projects/FY21 In-StatevsOut-State-Web-Main/admit-page.csv", header = T, stringsAsFactors = F)

kable(GA_thisWk_Admit %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         Location = ifelse(region == "Maine", "In-State", "Out-of-State"), 
         FY = ifelse(date < "2019-07-01", "FY19", 
                     ifelse(date > "2020-06-30", "FY21", "FY20"))) %>% 
  group_by(FY, Location) %>% summarise(UPV = sum(uniquePageviews)) %>% 
  spread(FY, UPV) %>% 
  select(-FY21) %>% 
  mutate(PctDif= paste0(round((FY20-FY19)/FY19 * 100,2),"%"),
         FY19 = prettyNum(FY19, big.mark = ","), 
         FY20 = prettyNum(FY20, big.mark = ",")) )
```

## Conclusions

* In FY20, traffic to the University's main landing page saw a drop in unique pageviews, down 6.75% from out-of state visitors and down 6% from in-state visitors from FY19. 

* In FY20, traffic from out-of-state visitors to the Office of Admissions' main landing page saw a slight increase in unique pageviews,  up by nearly 1%, while in-state visitors dropped by  18% in the same time period.

#

\href{https://www.wrike.com/open.htm?id=562722425}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/FY21-web-traffic-main-admissions-comparison-by-region}{{\color{blue}{\underline{Github Repository}}}}
